---
title: "himym_episodes"
author: "Ghinwa Moujaes"
date: "04/01/2022"
output: html_document
---


Let's start by taking a look at the dataset 

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)


df_episodes <- read_csv("../Data Notebooks/himym_episodes_ratings/himym_episodes.csv")
df_imdb <- read_csv("../Data Notebooks/himym_episodes_ratings/himym_imdb.csv")
```
We can see that in the first df, we have:
- Season
- Episode # in Season
- Episode # Overall
- Title
- Director
- Writers
- Original Air Date
- Production Code
- Number of US Viewers
```{r}
head(df_episodes, n = 12)
summary(df_episodes)
```
For the second df, we have:
- Season
- Episode Number
- Title
- Original Air Date
- IMDB Rating
- Total Votes
- Description 

```{r}
head(df_imdb)
```


***Questions for Explanatory Analysis*** 

How many episodes do we have per Season?
```{r}
#How many episodes do we have per season?
g1 <- df_episodes %>% 
  count(season) %>% 
  ggplot(aes(x = as.factor(season), 
             y = n)) + 
  geom_col(aes(fill = as.factor(season)), 
           stat = "identity") + 
  theme_light() + 
  geom_text(aes(label = n), 
            vjust = - 0.45, 
            fontface = "bold", 
            alpha = 0.5) + 
  labs(x = "Season", 
       y = "Number of Episodes", 
       title = "Number of Episodes per Season") + 
  theme(legend.position = "none", 
        plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16)) + 
  scale_y_continuous(labels = NULL,
                     limits = c(0, 27)) + 
  scale_fill_brewer(palette = "YlOrRd")

ggsave("HIMYM_graphs/episodes_per_season.jpeg")
```

What are the 10 most watched episodes? What is the average watch rate?
```{r}
total_avg <- mean(df_episodes$us_viewers)


df_episodes %>% 
  group_by(season) %>% 
  summarize(avg_viewers = mean(us_viewers)) %>% 
  rbind(data.frame(
    season = "average",
    avg_viewers = total_avg
  )) %>% 
  mutate(season = as.factor(season),
         color_code = ifelse(avg_viewers < total_avg, 
                        "red",
                        "blue")) %>% 
  ungroup()  %>% 
  ggplot(aes(x = season, 
             y = avg_viewers, 
             fill = color_code)) + 
  geom_col(stat = "identity") + 
  theme_classic() + 
    labs(x = "Season", 
       y = "Average Number of US Viewers", 
       title = "Average Number of US Viewers per Season") + 
  theme(legend.position = "right", 
        plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16)) + 
  scale_y_continuous(labels = scales::comma) + 
  scale_fill_manual(
    name = "",
    values = c("darkred", "lightblue"), 
    labels = c("Viewes Higher than \n Overall Average", 
               "Viewers Lower than \n Overall Average"))

ggsave("HIMYM_graphs/avg_views_per_season.jpg")
```
- Correlation between Total Votes & IMDB Rating --> Not a super useful graph
```{r}
df_imdb %>% 
  ggplot(aes(x = total_votes,
             y = imdb_rating,
             color = as.factor(season))) + 
  geom_point()
```

- Rating per Season:

```{r}
#Make More Aesthetic & Change Color Scheme
df_imdb %>% 
  ggplot(aes(x = as.factor(season),
             y = imdb_rating,
             color = as.factor(season))) + 
  geom_boxplot() +
  stat_summary(fun.y=mean, 
               aes(label = round(..y.., 2)),
               geom = "text",
               color="black", fill="black",
               fontface = "bold", 
               position = position_dodge()) +
  theme_classic() + 
  geom_jitter() + 
  theme(legend.position = "none") + 
  scale_color_brewer(palette = "RdYlBu") + 
  labs(title = "Average Rating per Season", 
       y = "Season", 
       x = "IMDB Rating") + 
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16))

ggsave("HIMYM_graphs/average_rating_per_season.jpeg")

```
- How many people voted each Season:
```{r}
#Make More Aesthetic, change Color Scheme, play with outliers
df_imdb %>% 
  ggplot(aes(x = as.factor(season),
             y = total_votes,
             color = as.factor(season))) + 
  geom_boxplot() + 
  theme_classic() + 
  geom_jitter() + 
  theme(legend.position = "none") + 
  scale_color_brewer(palette = "YlOrRd")
```

- Correlation between IMDB Rating & Num of US Viewers

```{r}
select(df_episodes, season, episode_num_in_season, us_viewers) %>% 
  rename(episode_num = "episode_num_in_season") %>% 
  full_join(select(df_imdb, season, episode_num, imdb_rating)) %>% 
  ggplot(aes(x = imdb_rating, 
             y = us_viewers)) + 
  geom_point() + 
  geom_smooth()

```

- Corr plot: What is the correlation between ratings, us-viewers & imdb votes?

```{r}
col_pal <- colorRampPalette(c("red", "white", "blue"))(100)
         

#Not sure how to change colors. :(                   
                            
select(df_episodes, season, episode_num_in_season, us_viewers) %>% 
  rename(episode_num = "episode_num_in_season") %>% 
  inner_join(select(df_imdb, season, episode_num, imdb_rating, total_votes)) %>%
  select(us_viewers, imdb_rating, total_votes) %>% 
  rename("Number of \nUS Viewers" = "us_viewers",
         "IMDB Rating" = "imdb_rating", 
         "Number of \nTotal Votes" = "total_votes") %>% 
  cor() %>% 
  corrplot::corrplot.mixed(lower.col = "black",
                           title = "Correlation plot",
                           mar=c(0,0,2,4)) 
```

- Number of Viewers per Date:

```{r}
df_episodes %>% 
  ggplot(aes(x = as.Date(original_air_date),
             y = us_viewers)) + 
  geom_col(aes(fill = as.factor(season))) + 
  theme_classic() + 
  scale_y_continuous(labels = scales::comma) + 
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") + 
  scale_fill_brewer(palette = "RdYlBu") + 
  labs(title = "Number of US Viewers vs. Release Dates",
       y = "US Viewers", 
       x = "Release Date",
       fill = "Season") + 
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16)) 

ggsave("HIMYM_graphs/viewers_per_release_date.jpeg")
```

```{r}
df_episodes %>% 
  ggplot(aes(x = as.Date(original_air_date),
             y = us_viewers)) + 
  geom_col(aes(fill = as.factor(lubridate::year(as.Date(original_air_date))))) + 
  theme_classic() + 
  scale_y_continuous(labels = scales::comma) + 
  scale_x_date(date_breaks = "1 year",
               date_labels = "%Y") + 
  scale_fill_brewer(palette = "RdYlBu") + 
  labs(title = "Number of US Viewers vs. Release Dates",
       y = "US Viewers", 
       x = "Release Date") + 
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16)) 
```


- Total Number of US Viewers per Year 
```{r}
df_episodes %>% 
  mutate(year = lubridate::year(as.Date(original_air_date))) %>% 
  group_by(year, season) %>% 
  summarize(total_viewers = sum(us_viewers)) %>% 
  ggplot(aes(x = as.factor(year), 
             y = total_viewers)) + 
  geom_col(aes(fill = as.factor(season)),
           stat = "identity") + 
  scale_y_continuous(labels = scales::comma) + 
  scale_fill_brewer(palette = "RdYlBu") + 
  labs(title = "Total Number of US Viewers per Year",
       y = "US Viewers", 
       x = "Year of Release Date",
       fill = "Season") + 
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16)) 

ggsave("HIMYM_graphs/viewers_per_release_year.jpeg")
```


- How many episodes came out each month?
```{r}
df_episodes %>% 
  mutate(month = lubridate::month(as.Date(original_air_date))) %>% 
  group_by(month) %>% 
  summarise(num_episodes_released = n()) %>% 
  ggplot(aes(x = as.factor(month),
             y = num_episodes_released,
             fill = as.factor(month))) + 
  geom_col(stat = "identity") + 
  labs(title = "Episodes Released per Month",
       y = "Number of Episodes Released", 
       x = "Month of Year") + 
  theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16), 
        legend.position = "none") + 
  scale_fill_brewer(palette = "YlOrRd") + 
  scale_x_discrete(labels = c("1" = "January",
                              "2" = "February",
                              "3" = "March",
                              "4" = "April",
                              "5" = "May",
                              "6" = "June",
                              "7" = "July",
                              "8" = "August",
                              "9" = "September",
                              "10" = "October",
                              "11" = "November",
                              "12" = "December"
                              ))

ggsave("HIMYM_graphs/episodes_released_per_month.jpeg")
```

- Text Mining on Episode Descriptions:
  - Most Used Words
  - Topic Modelling?
  - Words that can predict the number of viewers
  - Correlation between number of times love is in the description & viewer count/IMDB Rating


```{r}
library(tidytext)
library(tm)
library(qdap)
#library(RGraphViz)

df_text <- df_imdb %>% 
  select(season, episode_num, desc)

#Clean the text
df_text$text <- tolower(df_text$desc)
df_text$text <- tm::removeNumbers(df_text$text)

#Remove all punctuation 
df_text$text <- str_replace_all(df_text$text, pattern = "[[:punct:]]", " ")

#Remove all stopwords
df_text$text <- tm::removeWords(df_text$text,
                                stopwords::stopwords("english"))


#What are the 25 most frequent terms?
qdap::freq_terms(text.var = df_text$text, 
           top = 25)

#TF-IDF. Let's assume that each Document is an episode here

## Step 1. Tokenize:
df_text_episodes <- df_text %>% 
  unnest_tokens(words, text) %>% 
  count(season, episode_num, words, sort = TRUE) %>% 
    filter(words != c("s", "t"))


#Step 2: Bind-TFIDF Function
df_tfidf_episodes <- df_text_episodes %>% 
  bind_tf_idf(words, episode_num, n)

#What are the most used terms in this case?
df_tfidf_episodes %>% 
  arrange(desc(tf_idf))

#TF-IDF. Let's assume that each Document is a season here
df_text_seasons <- df_text %>% 
  unnest_tokens(words, text) %>% 
  filter(words != c("s", "t")) %>% 
  count(season, words, sort = TRUE)

#Step 2: Bind-TFIDF Function
df_tfidf_seasons <- df_text_seasons %>% 
  bind_tf_idf(words, season, n)

#What are the most used terms in this case?
df_tfidf_seasons %>% 
  arrange(desc(tf_idf))
```


We can see the most frequently used important words:
- Ted
- Barney
- Robin
- Marshall
- Lily
- Wedding
- Date
- Gang
- Relationship
- Night


According to the TF-IDF by episode, the most important words are:
- Slap
- Thanksgiving
- Future
- Texting
- Relationships
- Holding
- Received
- Rid
- Another
- Blind

According to the TF-IDF by episode, the most important words are:
- Zoey
- GNB
- Kevin
- Daphne
- Abby
- Island
- Stella
- Farhamton
- Nora
- Another


```{r}
#Good Start now consider which words we should consider "stop-words" and how to better visualize this

season_words <- df_tfidf_seasons %>% 
  group_by(season) %>%
  #Take the top ten most frequent words per season
  top_n(n = 10) %>% 
  ungroup()

df_tfidf_seasons %>% 
  group_by(season) %>% 
  #Take the top ten most frequent words per season
    top_n(n = 10) %>% 
  ggplot(aes(x = tf_idf, 
             y = forcats::fct_reorder(as.factor(words), tf_idf),
             fill = as.factor(season)
             )) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~as.factor(season), 
             ncol = 3,
             scales = "free") + 
  labs(x = "tf-idf", 
       y = "")
  
```

(The below doesn't say much so I would just remove/ignore it for now)

Let us try to find whether there is a correlation between the number of times each of these words comes up and their IMDB rating and/or number of US viewers
```{r}
df_text <- df_text %>% 
  mutate(
    ted = str_count(text, pattern = "ted"), 
    barney = str_count(text, pattern = "barney"),
    robin = str_count(text, pattern = "robin"), 
    marshall = str_count(text, pattern = "marshall"),
    lily = str_count(text, pattern = "lily"), 
    wedding = str_count(text, pattern = "wedding"),
    date = str_count(text, pattern = "date"),
    gang = str_count(text, pattern = "gang"), 
    relationship = str_count(text, pattern = "relationship"),
    night = str_count(text, pattern = "night")
  )

df_temp <- df_episodes %>% 
  select(season, episode_num_in_season, us_viewers) %>% 
  rename(episode_num = "episode_num_in_season") %>% 
  inner_join(select(df_imdb, season, episode_num, imdb_rating)) %>% 
  inner_join(df_text) %>% 
  select(us_viewers, ted, barney, robin, marshall, lily, wedding, date, gang, relationship, night)
  
#Maybe corrplot is not the best way to visualize the correlation
corrplot::corrplot(cor(df_temp[,1:11])[1:11,1,drop = FALSE],
                   method = "color", 
                   cl.pos = "n",
                   addCoef.col = 'grey50')
```

- Topic Modeling:
```{r}
library(topicmodels)

#For topic Modeling, we need to introduce the df in the tf-idf format but also in a DTM format
df_seasons_dtm <- df_tfidf_seasons %>% 
  filter(!(words %in% c("robin", "lily", "marshall", "ted", "barney", "s", "meanwhile", "t", "get", "gets", "tries")))  %>% 
  cast_dtm(season, words, n)

seasons_lda <- 
  LDA(df_seasons_dtm, 
      k = 4)

seasons_topics <- tidy(seasons_lda, matrix = "beta") %>% 
  group_by(topic) %>% 
  slice_max(beta, n = 5) %>% 
  ungroup() %>% 
  arrange(topic, beta)

seasons_topics %>% 
  ggplot(aes(beta, 
             term, 
             fill = as.factor(topic))) +
  geom_col(show.legend = FALSE) + 
  facet_wrap(~ topic,
             scales = "free") + 
  scale_y_reordered() + 
  labs(title = "Topic Modeling Results - 4 Groups", 
       x = "", 
       y = "Term") + 
    theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16), 
        legend.position = "none")

ggsave("HIMYM_graphs/topic_modeling_4groups.jpeg")
```
```{r}
seasons_lda <- 
  LDA(df_seasons_dtm, 
      k = 5)

seasons_topics <- tidy(seasons_lda, matrix = "beta") %>% 
  group_by(topic) %>% 
  slice_max(beta, n = 5) %>% 
  ungroup() %>% 
  arrange(topic, beta)

seasons_topics %>% 
  ggplot(aes(beta, 
             term, 
             fill = as.factor(topic))) +
  geom_col(show.legend = FALSE) + 
  facet_wrap(~ topic,
             scales = "free") + 
  scale_y_reordered() + 
  labs(title = "Topic Modeling Results - 5 Groups", 
       x = "", 
       y = "Term") + 
    theme_classic() + 
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16), 
        legend.position = "none")

ggsave("HIMYM_graphs/topic_modeling_5groups.jpeg")
```


```{r}
#How much is each topic represented in each Chapter?
tidy(seasons_lda, 
     matrix = "gamma")

#What is the best way to visualize this?
tidy(seasons_lda, 
     matrix = "gamma") %>% 
  ggplot(aes(x = topic,
             y = gamma,
             fill = document)) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~document) + 
  labs(title = "Topic Prevalence per Season",
       x = "Topic", 
       y = expression(gamma)) + 
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5, 
                                  face = "bold", 
                                  size = 16)) 

```
- What words tend to correlate together: https://www.tidytextmining.com/ngrams.html 

- Sentiment Analysis
```{r}
#What are the words that imply "joy" most widely used in the descriptions?

nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

df_text_episodes %>%
  rename(word = "words") %>% 
  inner_join(nrc_joy) %>% 
  count(word, sort = TRUE)

#What are the words that imply "sadness" most widely used in the descriptions?
nrc_sadness <- get_sentiments("nrc") %>% 
  filter(sentiment == "sadness")

df_text_episodes %>% 
  rename(word = "words") %>% 
  inner_join(nrc_sadness) %>% 
  count(word, sort = TRUE)

```


#This is good to learn but I wouldn't show it because it's a bit contradictory to saying this is a "comedy" series

```{r}
df_sentiments <- df_text_episodes %>% 
  rename(word = "words") %>% 
  inner_join(get_sentiments("bing")) %>% 
  pivot_wider(id_cols = 1:3, 
              names_from = sentiment, 
              values_from = n, 
              values_fill = 0.00) %>% 
  group_by(season, episode_num) %>% 
  summarise(positive = sum(positive),
            negative = sum(negative)) %>% 
  mutate(sentiment = positive - negative)


df_sentiments %>% 
  ggplot(aes(x = episode_num,
             y = sentiment,
             fill = season)) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(~season, 
             ncol = 2, scales = "free")

```

