---
title: "spotify_charts"
author: "Ghinwa Moujaes"
date: "14/05/2021"
output: html_document
---

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
```

It is a bit easier to read the data in R as we do not have to recreate the table from scratch. However, as shown by the message received, we need to be careful what type most columns are.
Song Rank & Number of streams are read as doubles as intended. 
However, chart_date is not read as a date. Make sure to specify the right format based on what is available!
```{r}
#reading the data
spotify_charts <- read_csv("spotify_charts.csv")

#read chart_date in date format
spotify_charts$chart_date <- as.Date(spotify_charts$chart_date, format = "%d/%m/%Y")
```

Find out for how many dates we have charts:
```{r}
sort(unique(spotify_charts$chart_date))
paste("Number of days we have different charts for:", length(unique(spotify_charts$chart_date)))
```

```{r}
paste("Number of countries we have different charts for:", length(unique(spotify_charts$country)))
```

The following tells us for each date, how many charts do we have?
```{r}
spotify_charts %>% 
  group_by(chart_date) %>% 
  summarize(num_of_charts = n_distinct(country))
```
For each country, how many dates do we have?
```{r}
spotify_charts %>% 
  group_by(country) %>% 
  summarize(num_of_charts = n_distinct(chart_date))
```
On average, we have 31.48515 charts per date. 
On average, we have 113.5714 charts per country

```{r message=FALSE}
spotify_charts %>% 
  group_by(chart_date) %>% 
  summarize(num_of_charts = n_distinct(country)) %>% 
  summarize(average_charts_per_date = mean(num_of_charts))

spotify_charts %>% 
  group_by(country) %>% 
  summarize(num_of_charts = n_distinct(chart_date)) %>% 
  summarize(average_charts_per_country = mean(num_of_charts))
```

```{r}
spotify_charts %>% 
  group_by(chart_date) %>% 
  filter(streams == max(streams))
```
To keep in line with what we did with SQL, we count how many times the top listened to song was in global vs. another country. 

```{r}
spotify_charts %>% 
  group_by(chart_date) %>% 
  filter(streams == max(streams)) %>% 
  group_by(country) %>% 
  summarize(num_of_times = n()) %>% 
  arrange(desc(num_of_times))
```

For the Global song charts, these are the top 10 songs that show up on different dates most often:

```{r}
spotify_charts %>% 
  filter(country == "Global") %>% 
  group_by(track_title) %>% 
  summarize(num_of_times_in_top_chart = n_distinct(chart_date)) %>% 
  arrange(desc(num_of_times_in_top_chart)) %>% 
  slice_head(n = 15)
```

For Switzerland:

```{r}
spotify_charts %>% 
  filter(country == "Switzerland") %>% 
  group_by(track_title) %>% 
  summarize(num_of_times_in_top_chart = n_distinct(chart_date)) %>% 
  arrange(desc(num_of_times_in_top_chart)) %>% 
  slice_head(n = 30)
```

For a specific date: 07-07-2017, which songs show up in the top 50 songs globally and in Spain at the same time

```{r}
spotify_charts %>% 
  filter(chart_date == "2017-07-07" & 
           country %in% c("Global", "Spain") & 
           song_rank <= 50) %>% 
  group_by(track_title) %>% 
  summarize(num_of_countries = n_distinct(country)) %>% 
  filter(num_of_countries == 2)
```

For each date, show the number of songs that Italy and Spain have in common in the top 50. 

```{r}
spotify_charts %>% 
  filter(country %in% c("Italy", "Spain")) %>% 
  group_by(track_title, chart_date) %>% 
  summarize(num_of_charts = n_distinct(country)) %>% 
  filter(num_of_charts == 2) %>% 
  group_by(chart_date) %>% 
  summarize(num_of_common_songs = n_distinct(track_title))
```

How many songs do we have that show up only once in our dataset? 

```{r}
spotify_charts %>% 
  group_by(track_title) %>% 
  summarize(num_of_charts = n_distinct(paste(country, chart_date))) %>% 
  filter(num_of_charts == 1) %>% 
  nrow()
```

